%-------------------------
% Resume in Latex
% Author : Jatin
% Based off of: https://github.com/jatin-sdev/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jatin} \\ \vspace{1pt}
    \small +91-8377912277 $|$ \href{mailto:jatin.sdev@gmail.com}{\underline{jatin.sdev@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jatin-sdev}{\underline{linkedin}} $|$
    \href{https://github.com/jatin-sdev}{\underline{github}}  $|$
    \href{https://jatin-portfolio-app.vercel.app/}{\underline{portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
 \resumeSubheading
      {Dronacharya College of Engineering}{Gurugram, Haryana}
      {Bachelor of Technology in Computer Science and IT; CGPA: 7.7} {2022 -- 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {WysBryx Technologies}{Remote}
      {Full Stack Developer Intern}{Nov. 2025 -- Present}
      \resumeItemListStart
        % SYNERGY PROJECT (Compressed to 3 lines)
        \resumeItem{Architected internal ERP \textbf{Synergy} using \textbf{MERN Stack} and \textbf{TypeScript} for 50+ users, automating weekly reporting via cron jobs to reduce manual effort by \textbf{40\%}.}
        \resumeItem{Secured sensitive HR data via \textbf{RBAC/JWT} middleware for 4 user roles and standardized \textbf{40+ RESTful endpoints} using \textbf{Swagger} for seamless integration.}
        \resumeItem{Engineered a reusable \textbf{Tiptap} rich-text editor with local caching, decreasing initialization latency by \textbf{30\%} to enhance content creation efficiency.}
        
        % GEBERIT PROJECT (Added 2 lines)
        \resumeItem{Developed \textbf{Geberit DXF Estimator}, a serverless platform using \textbf{React}, \textbf{Hono}, and \textbf{AWS Lambda} (SST) to automate complex CAD drawing analysis and material takeoffs.}
        \resumeItem{Designed a cost-effective single-table \textbf{DynamoDB} schema and implemented \textbf{AWS Cognito} auth, reducing infrastructure costs to \textbf{\$21/mo} while ensuring enterprise security.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeSubheading
        {Enterprise Orchestration Platform $|$ \textnormal{\emph{\href{https://github.com/jatin-sdev/Enterprise-Orchestration-Platform}{\underline{Repository}}}}}{}
        {TypeScript, React, Node.js, Express, MongoDB, Zustand, Zod, Jest}{}
          \resumeItemListStart
            \resumeItem{Architected a secure, scalable monorepo architecture using \textbf{Node.js} and \textbf{TypeScript}, implementing granular \textbf{RBAC} via \textbf{JWT} middleware to govern multi-level user permissions.}
            \resumeItem{Engineered a type-safe frontend ecosystem using \textbf{Zustand} for centralized state management and \textbf{Zod} for runtime validation, eliminating data inconsistency across complex modules.}
            \resumeItem{Standardized backend reliability by integrating \textbf{Swagger} for automated API documentation and establishing robust \textbf{Jest} testing pipelines for the RESTful infrastructure.}
          \resumeItemListEnd

      \resumeSubheading
        {Video Streaming Architecture $|$ \textnormal{\emph{\href{https://github.com/jatin-sdev/vidtube}{\underline{Repository}}}}}{}
        {Node.js, Express, MongoDB, Cloudinary, Bcrypt, JWT, Multer}{}
          \resumeItemListStart
            \resumeItem{Developed a high-performance backend handling complex data relationships using \textbf{MongoDB Aggregation Pipelines}, optimizing query execution time for video feeds.}
            \resumeItem{Implemented secure authentication utilizing \textbf{JWT} and \textbf{HttpOnly cookies} to prevent XSS attacks and manage user sessions effectively.}
            \resumeItem{Integrated \textbf{Cloudinary} for optimized video storage and retrieval, ensuring low-latency media delivery across varying bandwidths.}
          \resumeItemListEnd

      \resumeSubheading
        {E-Commerce Web Platform $|$ \textnormal{\emph{\href{https://github.com/jatin-sdev/mern-ecommerce-main}{\underline{Repository}}}}}{}
        {React, Redux Toolkit, Node.js, Stripe, Nodemailer, MongoDB}{}
          \resumeItemListStart
            \resumeItem{Built a feature-rich shopping platform using \textbf{Redux Toolkit} for global state management of carts and user profiles, reducing unnecessary re-renders.}
            \resumeItem{Integrated \textbf{Stripe API} to process secure transactions and implemented \textbf{Nodemailer} for automated OTP verification and order notifications.}
            \resumeItem{Designed a dynamic admin dashboard for real-time inventory management, supporting complex CRUD operations for product listings.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, Python, Java, SQL, HTML/CSS} \\
     \textbf{Frontend}{: React.js, Next.js, Redux Toolkit, TailwindCSS, Shadcn/ui} \\
     \textbf{Backend}{: Node.js, Express.js, REST API, JWT, Socket.io} \\
     \textbf{Databases}{: MongoDB (Mongoose), PostgreSQL (Drizzle ORM)} \\
     \textbf{DevOps \& Tools}{: Git, Docker, Postman, Swagger, Vitest, Jest}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
